---
title: "Blog_Fight"
output:
  html_document: default
  word_document: default
  pdf_document: default
date: "2023-12-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quantative Methods: Group Chicago

This report presents an analysis of economic indicators and their relationship with unemployment rates. The report is based on the study replicated by John Taylor who tried to prove that the more the government spends and invests, the higher the unemployment rate. Taylor used data between 1990-2010 in his analysis. In this report, we analyze the specific timeframe John Taylor utilized with periods that occurred earlier and later than the one he focused on to understand the criticism from Justin Wolfers. In order to complete this analysis, data on government spending, unemployment, and GDP was collected from FRED. An important distinction to make is that government spending is used as a percentage of GDP.

# Part 1: Clean Data

```{r clean}
# Read in data
unemployment <- read.csv("UNRATE.csv")  # Reading unemployment data from a CSV file
gdp <- read.csv("GDP.csv")  # Reading GDP data from a CSV file
spending <- read.csv("GCE.csv")  # Reading government spending data from a CSV file

# Rename Variables and Convert Dates
names(gdp) <- c("Date", "gdp")  # Renaming columns in the GDP dataset
gdp$Date <- as.Date(gdp$Date, format ="%Y-%m-%d")  # Converting the date column in GDP to Date format

names(spending) <- c("Date", "spending")  # Renaming columns in the spending dataset
spending$Date <- as.Date(spending$Date, format ="%Y-%m-%d")  # Converting the date column in spending to Date format

names(unemployment) <- c("Date", "percent")  # Renaming columns in the unemployment dataset
unemployment$Date <- as.Date(unemployment$Date, format ="%Y-%m-%d")  # Converting the date column in unemployment to Date format

# Merge Data
merged_dat <- merge(merge(gdp, spending, by = "Date"), unemployment, by = "Date")  # Merging all datasets by Date
merged_dat <- na.omit(merged_dat)  # Handling missing values by removing rows with any NA values

# Calculate spending as a percent of GDP
merged_dat$spending_gdp <- merged_dat$spending / merged_dat$gdp  # Creating a new column for spending as a percentage of GDP
```

# PART 2: Create Datasets

```{r datasets}
# Create dataset for Taylor's time frame and plot
taylor <- subset(merged_dat, Date >= as.Date("1990-01-01") & Date < as.Date("2010-10-01"))  # Subset for Taylor's time frame (1990-2010)
plot(taylor$spending_gdp * 100, taylor$percent, col = "blue", pch = 16, 
     xlab = "Government purchases as a percent of GDP", 
     ylab = "Unemployment rate", 
     main = "Taylor's Time Frame")  # Plotting a scatterplot for Taylor's time frame
```

#  PART 3: Plotting
```{r plot, echo=TRUE}
# Full dataset
plot(merged_dat$spending_gdp * 100, merged_dat$percent, col = "blue", pch = 16, 
     xlab = "Government purchases as a percent of GDP", 
     ylab = "Unemployment rate", 
     main = "Full Data Set")  # Plotting a scatterplot for the entire dataset

# Pre-Taylor
pre_taylor <- subset(merged_dat, Date < as.Date("1990-01-01"))  # Subset for time before Taylor's time frame
plot(pre_taylor$spending_gdp * 100, pre_taylor$percent, col = "blue", pch = 16, 
     xlab = "Government purchases as a percent of GDP", 
     ylab = "Unemployment rate", 
     main = "Pre-Taylor's Time Frame")  # Plotting a scatterplot for the time before Taylor's time frame

# Post-Taylor
post_taylor <- subset(merged_dat, Date >= as.Date("2010-10-01"))  # Subset for time after Taylor's time frame
plot(post_taylor$spending_gdp * 100, post_taylor$percent, col = "blue", pch = 16, 
     xlab = "Government purchases as a percent of GDP", 
     ylab = "Unemployment rate", 
     main = "Post-Taylor's Time Frame")  # Plotting a scatterplot for the time after Taylor's time frame
```


# PART 4: Regression Analysis

```{r regression, echo=TRUE}
# Adding indicator variables for each time frame
# Original dummy variables

years <- as.integer(format(merged_dat$Date, "%Y")) # Extract year and convert to integer
decades <- as.factor((years %/% 10) * 10 )
summary(lm(percent~spending_gdp*decades, data=merged_dat))

merged_dat$pre_taylor <- as.numeric(merged_dat$Date < as.Date("1990-01-01"))
merged_dat$taylor <- as.numeric(merged_dat$Date >= as.Date("1990-01-01") & merged_dat$Date < as.Date("2010-10-01"))
merged_dat$post_taylor <- as.numeric(merged_dat$Date >= as.Date("2010-10-01"))
merged_dat$Year <- as.numeric(format(as.Date(merged_dat$Date), "%Y"))
merged_dat$full_data= as.numeric(merged_dat$Year >= 1940 & merged_dat$Year < 2024)
# Decade dummy variables
merged_dat$decade_40s <- as.numeric(merged_dat$Year >= 1940 & merged_dat$Year < 1950)
merged_dat$decade_50s <- as.numeric(merged_dat$Year >= 1950 & merged_dat$Year < 1960)
merged_dat$decade_60s <- as.numeric(merged_dat$Year >= 1960 & merged_dat$Year < 1970)
merged_dat$decade_70s <- as.numeric(merged_dat$Year >= 1970 & merged_dat$Year < 1980)
merged_dat$decade_80s <- as.numeric(merged_dat$Year >= 1980 & merged_dat$Year < 1990)
merged_dat$decade_90s <- as.numeric(merged_dat$Year >= 1990 & merged_dat$Year < 2000)
merged_dat$decade_00s <- as.numeric(merged_dat$Year >= 2000 & merged_dat$Year < 2010)
merged_dat$decade_10s <- as.numeric(merged_dat$Year >= 2010)

plot_period <- function(data, period_var, period_name) {
  plot(data$spending_gdp[data[[period_var]] == 1], data$percent[data[[period_var]] == 1], 
       main = paste("Unemployment vs Government Spending -", period_name),
       xlab = "Government Spending (% of GDP)", ylab = "Unemployment Rate (%)", 
       col = "blue", pch = 20)
  abline(lm(percent ~ spending_gdp, data = data[data[[period_var]] == 1,]), col = "red")
}

# Plot for each decade and time period
par(mfrow = c(3, 4)) # Adjust the layout to fit all plots

# Plots by decade
plot_period(merged_dat, "decade_40s", "1940s")
plot_period(merged_dat, "decade_50s", "1950s")
plot_period(merged_dat, "decade_60s", "1960s")
plot_period(merged_dat, "decade_70s", "1970s")
plot_period(merged_dat, "decade_80s", "1980s")
plot_period(merged_dat, "decade_90s", "1990s")
plot_period(merged_dat, "decade_00s", "2000s")
plot_period(merged_dat, "decade_10s", "2010s")

# Plots by pre-Taylor, Taylor, and post-Taylor periods
plot_period(merged_dat, "pre_taylor", "Pre-Taylor")
plot_period(merged_dat, "taylor", "Taylor")
plot_period(merged_dat, "post_taylor", "Post-Taylor")
#plot full period

plot_period(merged_dat, "full_data", "full_data")
# Reset plot layout
par(mfrow = c(1, 1))

# Function to simulate cherry picking of correlations
simulate_cherry_picking <- function(num_replications = 1000, total_quarters = 256, min_quarters = 60) {
  cherry_picked_correlations <- numeric(num_replications)
  full_sample_correlations <- numeric(num_replications)
  
  for (i in 1:num_replications) {
    # Generate two series of random uncorrelated data
    x <- rnorm(total_quarters)
    y <- rnorm(total_quarters)
    
    # Store the correlation over the entire sample
    full_sample_correlations[i] <- cor(x, y)
    
    # Initialize max correlation for this replication
    max_correlation <- -Inf
    
    # Loop over possible cherry-picked ranges
    for (j in (total_quarters - min_quarters + 1):total_quarters) {
      start_quarter <- total_quarters - j + 1
      end_quarter <- total_quarters
      cherry_correlation <- cor(x[start_quarter:end_quarter], y[start_quarter:end_quarter])
      max_correlation <- max(max_correlation, cherry_correlation)
    }
    
    # Store the maximum cherry-picked correlation
    cherry_picked_correlations[i] <- max_correlation
  }
  
  list(cherry_picked = cherry_picked_correlations, full_sample = full_sample_correlations)
}

# Run the simulation
simulation_results <- simulate_cherry_picking()
semi_transparent_black <- rgb(0, 0, 0, alpha = 0.5)  # 50% transparent black

hist(simulation_results$cherry_picked, breaks = 50, col = "gold", main = "Cherry Picked vs. Full Sample Correlations", xlab = "Correlation")

hist(simulation_results$full_sample, breaks = 50, col = semi_transparent_black, xlab = "Correlation", add = TRUE)

# Add a legend
legend("topright", legend = c("Cherry Picked", "Full Sample"), fill = c("gold", semi_transparent_black))
# T-test to compare cherry picked correlations and full sample correlations
t.test_result <- t.test(simulation_results$cherry_picked, simulation_results$full_sample)

# Print the result of the t-test
print(t.test_result)
```